---
title: "Cryptography"
output: html_document
date: "2023-04-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Safety: bad things don't happen 
Liveness: good things happen eventually 

CIA: 
- Confidentiality: secrets stay secret (safety: the bad thing is unsecrecy)

- Integrity: Agents are who they say they are (safety: bad thing is impersonation) 

- Availability: Good thing happens eventually (basically liveness)

Now we must rigorously differentiate C and I. 

Hashing: 
Hashing is a technique to convert numerical value of arbitrary size (i.e no maximum value) 

```{r}
min_hash = function(n, max) {
  return(n %% max)
}

min_hash(4,2) # remainder is 0 
min_hash(9,3) # remainder is 0
min_hash(12,5) # remainder is 2 
min_hash(12,7) # remainder is 5

min_hash(11,10) == min_hash(21,10) #both have a remainder of 1, so this statement is TRUE. 

#this is a mathematical example of integrity, where 2 'agents' would confirm they both get the same number on each end. 
```

A *hash-based signature* is a technique where a numerical value of small size is computed from a large amount of numerical daata in such a manner that, if the overall data is changed, the hash is highly likely to change. 

They are used to allow us to validate executables online. 

# Modulus 

Review Question 1:

Consider the case of a social media account of a journalist who is sharing public information for which it is important that the public may access the information, and that the information be vetted.

Which of the following does the journalist NOT require?

A. Confidentiality B. Integrity C. Availability 

ANSWER: B. Integrity 

Review Question 2:
Consider the case of a whistleblower who, given the opportuntiy, would share information with a media outlet, but who does not want to be surveiled while sharing the information?

Which of the following does the whistleblower most strongly require?

A. Confidentiality B. Integrity C. Availability 

ANSWER: Availability 

Review Question 3 
Two of the following can be guaranteed mathematically in the context of a single transfer of information. Which cannot?

A. Confidentiality B. Integrity C. Availability

ANSWER: Availability 

Review Question 4
Which of the following is like liveness? 

A. Confidentiality B. Integrity C. Availability

C. Availability 

Which of the follow are like safety? 

A. Confidentiality and Integrity 

What is a hash-based signature? 

C - a numerical value of a fixed size, that may be compute over numerical data of any size. 


Review of Entropy: 

```{r}
numToBits = function(val){
  paste(tail(rev(as.integer(intToBits(val))), n =5), collapse = "")
}

numToBits(1)

intToBits(1)
```


```{r}
intToUtf8(65:90)
utf8ToInt("Z")
```
```{r}
substring("hello",1,1)
```

```{r}
ind_to_num = function(str, i)
{
  return(utf8ToInt(substring(str,i,i)))
}

ind_to_num("AAA",3)
```

```{r}
text_to_num <- function(str)
{
  retVal = 0 ;
  for (i in 1:nchar(str)) 
  {
    retVal = retVal + utf8ToInt(substring(str,i,i))
  }
  return(retVal)
}

text_to_num("hello")
```

```{r}
num_to_text <- function(n)
{
  retStr = ''
  char1 = as.integer(n / (2 ^ 8))
  retStr = paste(retStr, intToUtf8(char1), sep='')
  char2 = n - (char1 * (2 ^ 8))
  retStr = paste(retStr, intToUtf8(char2), sep='')
  return(retStr)
}

num_to_text(4050505)
```

```{r}
num_to_text <- function(n)
{
  retStr = ''
  char1 = as.integer(n /  (2 ^ 8))
  retStr = paste(retStr, intToUtf8(char1), sep='')
  char2 = as.integer(n %% (2 ^ 8))
  retStr = paste(retStr, intToUtf8(char2), sep='')
  return(retStr)
}

num_to_text(234203402340)
```

```{r}
textToNumr <- function(s)
{
  if (nchar(s) == 1)
  {
    return(utf8ToInt(substring(s,1,1)))
  }
  return(utf8ToInt(substring(s,1,1)) + 256 * textToNumr(substring(s,2,nchar(s))))
}
```

```{r}
textToNum <- function(s)
{
  retVal = 0
  for (i in 1:nchar(s))
  {
    retVal = retVal + utf8ToInt(substring(s,i,i)) * (2 ^ 8) ^ (nchar(s)-i)
  }
  return(retVal)
}

textToNum('hello')
```

```{r}
numToTextr <- function(n)
{
  if (n > 0)
  {
    return((paste0(rev(intToUtf8(n %% 256)),numToTextr(as.integer(n / 256)))))
  }
  return('')
}

numToTextr(448378203247)
```


