---
title: "cs_20230412"
output: html_document
date: "2023-04-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

April 12 2023 

RSA
(Our first deployable cryptography algorithm) 

Last week we did this: 

```{r}
textToNum <- function(s)
{
  val = substring(s,1,1)
  val = utf8ToInt(val)
  cs  = nchar(s)
  if (cs > 1)
  {
    rst = substring(s,2,cs)
    rst = textToNum(rst)
    val = val + 0x100 *  
  }
  return(val)
}

#we have a string and we want to turn into a number 
#we turn a part of that string into a number, and then smoosh those together #for a string of length greater than one 
#val = number 
# rst = rest of string 


```

```{r}
textToNum <- function(s)
{
  cs = nchar(s)
  v  = substring(s,1,1)
  v  = utf8ToInt(v)
  if (cs > 1)
  {
    r = substring(s,2,cs)
    r = textToNum(r)
    v = v + 0x100 * r
  }
  return(v)
}


textToNum('hello')
```

```{r}
textToNum <- function(s)
{
  cs = nchar(s)
  v  = substring(s,cs,cs)
  v  = utf8ToInt(v)
  if (cs > 1)
  {
    r = substring(s,1,cs-1)
    r = textToNum(r)
    v = v + 0x100 * r
  }
  return(v)
}

textToNum('hello')
```

```{r}
textToNum <- function(s)
{
  vn = 0
  cs = nchar(s)
  while (cs) {
    vs = substring(s,1,1)
    vn = vn * 0x100
    vn = vn + utf8ToInt(vs)
    s  = substring(s,2,cs)
    cs = nchar(s)
  }
  return(v)
}

textToNum('hello')
```

```{r}
textToNum <- function(s)
{
  cs = nchar(s)
  v  = substring(s,1,1)
  v  = utf8ToInt(v)
  if (cs > 1)
  {
    r = substring(s,2,cs)
    r = textToNum(r)
    v = v + 0x100 * r
  }
  return(v)
}
```

```{r}
numToText <- function(n)
{
  !n && return() #if n = 0, return nothing 
  v = n %% 0x100
  r = n /  0x100
  r = floor(r)
  v = intToUtf8(v)
  r = numToText(r)
  return(paste0(v,r))
}


```

```{r}
numToText <- function(n)
{
  !n && return()
  v = n %% 0x100
  r = n /  0x100
  r = floor(r)
  v = intToUtf8(v)
  r = numToText(r)
  return(paste0(r,v))
}

numToText <- function(n)
{
  !n && return()
  v = n %% 0x100
  r = n %/%  0x100
  r = floor(r)
  v = intToUtf8(v)
  r = numToText(r)
  return(paste0(v,r))
}
```

Written iteratively:
```{r}

numToText <- function(n)
{
  s = ''
  while (n) 
  {
    v = n %% 0x100
    n = n /  0x100
    n = floor(n)
    v = intToUtf8(v)
    s = paste0(v,s)
  }
  return(s)
}
```

```{r}
cs = nchar('string')

?nchar()
```

```{r}
tail <- function(s)
{
  return(substring(s,2,nchar(s)))
}

typeof(floor(145.34))

as.integer(floor(2.5))

typeof(floor(2.5))
```

A public-key cryptosystem is a technique to convert message of up to fixed size (that is, with a maximum value) to "cyphertext" - a numerical value that contains the information of a message, but not in a readable manner. To be a public-key system, any agent must be able to produce cyphertexts, but only the intended receiver may extract the original message from the cyper text.

```{r}
encrypt <- function(s, e)
{
  return(textToNum(s) ^ e)
}

decrypt <- function(s, d, n)
{
  v = (s ^ d) %% n
  return(numtoText(v))
}


```

write a function that makes prime numbers ( that is only divisible by 1 and itself). 

### warm-up: function that prints all the factors of the numbers 
```{r}
factor_finder = function(x)
{
  for (i in 1:x)
  {
    if((x %% i) == 0)
    {
      print(i)
    }
  }
}

factor_finder(100)
```
# function that generates a a prime number 

```{r}
is_prime = function(n) 
{
  factor_num = list()
  for (i in 1:n)
  {
    if((n %% i) == 0)
    {
      factor_num = append(factor_num,i)
    }
  }
  
    if(length(factor_num) == 2)
    {
        return(TRUE)
    }
    else
    {
      return(FALSE)
    }
}


get_prime = function()
{
  prime_check = FALSE 
  while(prime_check == FALSE)
  {
   x = sample(1:1000,1)
   prime_check = is_prime(x)
   if(prime_check)
    {
      return(x)
    }
  }
}

#testing get_prime() 
get_prime()

```

# least common multiple 

```{r}
lcm = function(x,y)
{
  big = max(x,y)
  little = min(x,y)
  multiple = big
  while(multiple %% little != 0)
  {
    multiple = multiple + big
  }
  return(multiple)
}
  
#check
lcm(6,8)
```

## calvin's primarily function:  
```{r}
primality <- function(n) 
{
  i = 2
  while (i < n)
  {
    if (n %% i == 0)
    {
      return(FALSE)
    }
    i = i + 1
  }
  return(TRUE)
}

#For each integer i in this range, the function checks whether n is divisible by i using the modulo operator (%%). If n is found to be divisible by any number in this range, it cannot be prime and the function returns FALSE.

primality(71)

71 %% 2
```


## Co-primality 

Two numbers are co-prime if they do not have any common factors other than 1.
```{r}
coprimality <- function(n,m) 
{
  i = 2
  while (i < n && i < m)
  {
    if (n %% i == 0 && m %% i == 0)
    {
      return(FALSE)
    }
    i = i + 1
  }
  return(TRUE)
}



coprimality(3,4)
```


```{r}
if(gcd)
```


** this works 
```{r}
primality <- function(n) 
{
  for (i in 2:sqrt(n))
  {
    n %% i == 0 && return(FALSE)
  }
  return(TRUE)
}

primality(7)
```

## greatest common denominator 
gcd = the highest number that divides all the given integers.
```{r}
gcd <- function(n, m)
{
  a = max(n,m)
  b = min(n,m)
  if (b == 0)
  {
    return(a)
  }
  return(gcd(b, a %% b))
}

gcd(3,7)
```



```{r}
coprimality <- function(n,m) 
{
  return(gcd(n,m)==1)
}

coprimality(5,7)
```

```{r}
lambda <- function(p, q) 
{
  lcm <- function(n, m)
  lcm(p - 1, q - 1)
}

lambda(p,q)
```

# KEY GENERATION in 5 STEPS 

1. Compute two prime numbers p and q: 
```{r}
p = get_prime()
q = get_prime()
```

2. Compute the product of these primes n: 
```{r}
n = p*q 
```

3. Compute λ(n) "Carmichael's totient function"
```{r}
lambda <- function(p, q) 
{
  lcm <- function(n, m) { ... }
  lcm(p - 1, q - 1)
}
```

4. Compute a value e co-prime with λ(n)
```{r}
getCoPrime <- function(n, s=3) 
{
  p <- sample(10 ^ s:10 ^ (s + 1), 1)
  while (!coprimality(p, n))
  {
    p <- p + 1
  }
  return(p)
}
# OR e = 3 OR e = 655327

```


5. Compute d, the modular multiciplicate inverse of e modulo λ(n)


```{r}
#my function: 
modularmultiplicativeInverse = function(n,b)
{
  for(m in 0:(1-b))
  {
    if(modMult(n,m,b) == 1)
    {
      return(m)
    }
  }
  return('fail')
}

#calvin's function 

mMI <- function (a, b)
{
  r = c(a,b)  # old, new
  s = c(1,0)
  t = c(0,1)
  while (r[2])
  {
    q = floor(r[1] / r[2])
    r = c(r[2], r[1] - q * r[2])
    s = c(s[2], s[1] - q * s[2])
    t = c(r[2], t[1] - q * t[2])
  }
  return(s[1] %% b)
}
```


exponentiation by repeated multiplication
```{r}
exp <-function(n,e)
{
  !e && return(1)
  return(n*exp(n,e-1))
}


mExp = function(n,e,x)
{
  !e && return(1)
  
  for(m in 1:(n %% x))
  {
    result = (n %% x)*mExp(n,e-1,x)
  }
  return(result)

  #a = n %% x 
  #b = a*mExp(n,e-1,x)
  #c = b*mExp(n,e-1,x)
}



mExp(40,3,14)
```
calvin's code: 

```{r}
mExp <- function(x, p, m)
{
  !p && return(1)
  x = (x %% m)
  t = mExp(x, p - 1, m)
  x = (x * (t %% m))
  x = x %% m
  return(x)
}

mExp(2,6,10)
```


```{r}
funcMakr <- function(b) {
    frst <- function(s){
      x = textToNum(s)
      return(mExpS(x,e,n))
    }
    scnd <- function(x) {
      v = mExpS(x,d,n)
      return(numToText(v))
    }
    if (b){
      return(frst)
    } else {
      return(scnd)
    }
  }
```



```{r}
keygen <-function(s=1)
{
  getPrime <- function(s=3) 
  {
    primality <- function(n) 
    {
      n %% 2 == 0 && return(FALSE)
      for (i in 1:ceiling(sqrt(n) / 2)) 
      {
        n %% (2 * i + 1) == 0 && return(FALSE)
      }
      return(TRUE)
    }
    p <- sample(10 ^ s:10 ^ (s + 1), 1)
    while (!primality(p))
    {
      p <- p + 1
    }
    return(p)
  }

  lcm <- function(n, m) 
  {
    gcd <- function(n, m)
    {
      if(m) gcd(m, n %% m) else n
    }
    (n * m) / gcd(max(n,m), min(n,m))
  }
  mMI<-function(a,b)
  {
    v = c(a,b,1,0,0,1)
    while(v[2]){
      v=c(
        v[2], v[1] - v[1] %/% v[2] * v[2],
        v[4], v[3] - v[1] %/% v[2] * v[4],
        v[2], v[5] - v[1] %/% v[2] * v[6])
    }
    return(v[3]%%b)
  }
  d = 1
  while (d == 1 || d < 256)
  {
    ps = c(getPrime(s),getPrime(s))
    n  = ps[1] * ps[2]
    ln = lcm(ps[1]-1,ps[2]-1)
    e  = 3
    d  = mMI(e, ln)
  }

  textToNum <- function(s)
  {
    if (nchar(s) > 1)
    {
      return(utf8ToInt(substring(s,1,1)) + 
        256 * textToNum(substring(s,2,nchar(s))))
    }
    return(utf8ToInt(substring(s,1,1)))
  }

  numToText <- function(n)
  {
    if (n > 0)
    {
      return(paste0(
        intToUtf8(n %% 256),
        numToText(n %/% 256)))
    }
    return('')
  }

  mExp <- function(x, p, m)
  {
    !p && return(1)
    x = (x %% m)
    if  (p %% 2) 
    {
      t = x * mExp(x, p - 1, m)
    } else {
      t = mExp(x * x, p / 2, m)
    }
    return(t %% m)
  }

  funcMakr <- function(b)
  {
    frst <- function(s)
    {
      x = textToNum(s)
      return(mExp(x,e,n))
    }
    scnd <- function(x)
    {
      v = mExp(x,d,n)
      return(numToText(v))
    }
    if (b)
    {
      return(frst)
    } else {
      return(scnd)
    }
  }
  return(funcMakr)
}
```

testing: 
```{r}
fs = keygen()
encrypt = fs(1)
decrypt = fs(0)
decrypt(encrypt("a"))

#problem: it works for single chars, not a string.
```

