---
title: "LTL_R_part2"
output: pdf_document
date: "2023-04-06"
---

# Cybersecurity : Week 12 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Globally 
Future 
Release 
Weak_Until 
Mighty_Release

What is material implication ?
a -> b 

a b   a -> b 
T T   T
T F   F
F T   T
F F   T

```{r}
conjunction = function(e1,e2)
{
  return(e1(t))
}
```



```{r}
text_to_num = function(str)
{
  retVal = 0
  for(i in 1:nchar(str))
  {
    retVal = retVal + utf8ToInt(substring(str,i,i))
  }
  return(retVal)
}

text_to_num("hello")
#Takes one part of string and converts to numbers 
```

We should be suspicious of this output, 532 is a very small value for a string of length 5. 

- How many strings of length 5 are there? A LOT 
- how many string of length 5 are alphabetically before "hello"? 
- how many string of length less that 5 are there? 


```{r}
num_to_text = function(n)
{
  retStr = ''
  char1 = as.integer(n/(2^8))
  retStr = paste(retStr, intToUtf8(char1), sep = '')
  char2 = as.integer(n %% (2^8))
  retStr = paste(retStr, intToUtf8(char2), sept ='')
  return(retStr)
}
```

num_to_text 
```{r}

nums = c(1:26)       
letters = c('a','b','c','d','e','f','g','h','i','j','k','l','m','n','o','p','q','r','s','t','u','v','w','x','y','z')

codex = data.frame(nums, letters)

str = "hello"

for(i in 1:nchar(str))
{
  letter = substr(str,i,i)
}

num_to_text = function(n)
{
  return_string = '' 
}



```

text_to_num 
```{r}

text_to_num = function(n) 
{
  
}
```



```{r}
text_to_num = function(string)
{
ind_to_num = function(str, i)
{
  return(utf8ToInt(substring(str,i,i)))
}

}

```

```{r}
intToUtf8(256)
```

```{r}


```

