---
title: "LTL in R"
author: "Charles Hanks, in collaboration with Jesse, Ben, and Danny"
date: "2023-03-17"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Initial List; 
```{r}
t = list('a','a','a','b')
```

ATOMIC PROPOSITION: 

```{r}
ap = function(p){
  f = function(t)
  {
    return(grepl(p,t[1], fixed = TRUE))
  }
  return(f)
}

### TEST

a = ap('a')
b = ap('b')
```

NEXT: 

a holds in the next time 

Xa
```{r}
neXt <- function(exp)
{
  f = function(t)
    {
    len = length(t)
    if (len > 1)
      {
      return(exp(t[2:len]))
      } 
    else 
      {
        return(exp(t))
      }
    }
  return(f)
}

```


Upgrading neXt function to have ability to execute multi-nexts: 
```{r}
neXt = function(exp,sup =1)
{
  f = function(t)
  {
    len = length(t)
    if(len > sup)
    {
      return(exp(t[(sup+1):len]))
    }
    else 
    {
      return(exp(t[len:len]))
    }
  }
  return(f)
}

### TEST

Xa = neXt(a)
Xb = neXt(b)

neXt(Xa)(t)

#is the next letter in the word b? 
neXt(ap('b'))(t)

#is the 3rd next letter b? 
neXt(ap('b'),3)(t)
```


NEGATION:

not a

¬ a
```{r}
negation = function(exp){
  f = function(t)
  {
    return(!exp(t))
  }
  return(f)
}

t
a = ap('a')
b = ap('b')

negation(b)(t)



```


DISJUNCTION: 

a OR b 

a ∨ b
```{r}
disjunction = function(exp1,exp2)
{
  f = function(t)
  {
    return(exp1(t) || exp2(t))
  }
  return(f)
}

### TEST 

a = ap('a')
b = ap('b')

disjunction(a,b)(t)
disjunction(Xa,Xb)(t) 

t3 = list('c','a','c')
disjunction(neXt(a),b)(t3)

NXaDNxb = disjunction(negation(neXt(ap('b'))), negation(Xa))
NXaDNxb(t) 

neXt(NXaDNxb,2)(t)

```


CONJUNCTION: 

a AND b 

a ∧ b
```{r}
conjunction = function(exp1,exp2)
{
  f = function(t)
  {
    return(exp1(t) && exp2(t))
  }
  return(f)
}

### TEST 

t = list('a','a','a','ab')

# a test that should result in false 
conjunction(ap('a'),ap('ab'))(t)

# a test that should result in true 
neXt(conjunction(neXt(a),b),3)(t)


```

IMPLICATION:

if a then b

a → b 
```{r}
implication = function(exp1,exp2)
{
    f = function(t)
    {
    result = FALSE
      if(exp1(t) == FALSE && exp2(t) == FALSE)
      {
        result = TRUE  
      }
      else if (exp1(t) == FALSE && exp2(t) == TRUE)
      {
        result = TRUE 
      }
      else if (exp1(t) == TRUE && exp2(t) == FALSE)
      {
        result = FALSE 
      }
      else if (exp1(t) == TRUE && exp2(t) == TRUE)
      {
        result = TRUE 
      }
      else 
      {
        result = FALSE
      }
    return(result)
    }
  return(f)
}

### TEST 

t = list('a','a','b','d')

implication(b,Xb)(t)
implication(a,Xb)(t)

t5=list('a','b','c','d')
implication(b,a)(t5)
```

UNTIL: 

a holds unless b holds, and b must hold at some future time 

a U b 
```{r}
Until <-function(exp1,exp2)
{
  f <- function(t)
  {
    len = length(t)
    if (len > 1 & exp1(t))
    {
      # if exp1 holds and there's trace left, we look at the rest of the trace
      return(Until(exp1,exp2)(t[(2):len]))
    } else {
      # otherwise, either exp2 holds or the until is false
      return(exp2(t))
    }
  }
  return(f)
}

### TEST 

t = list('a','a','a','b')
Until(a,b)(t)
t = list('b','a','a','a','c','c','c')
Until(a,b)(t)
```

GLOBAL: 

a holds in all future times 

G a ≡ a ∧ (a → Xa)
```{r}
Global = function(exp)
{
  f = function(t)
  {
    len = length(t)
    for(i in 1:len)
    {
      if(conjunction(exp,implication(exp,neXt(exp)))(t[i:len])) # a ^ a -> Xa
      {
          result = TRUE
      }
      else 
      {
          result = FALSE 
          break 
      }
    }
    return(result)
  }
  return(f)
}

#### TEST 

t = list('a','a','a','b','a','a')
Global(a)(t)
t2 = list('a','a','a','a','a','a')
Global(a)(t2)

```

FUTURE: 

a must hold eventually 

F a ≡ true U a
```{r}
Future = function(exp) 
{
  f = function(t)
  {
    result = FALSE
    len = length(t)
    for (i in 1:len)
    {
      if (exp(t[i]))
      {
        result = TRUE 
        break
      }
      else
      {
        result = FALSE 
      }
      
    }
    return(result)
  }
  return(f)
}

### TEST 

t = list('a','a','a','b','a','a')
Future(b)(t)

t1 = list('c','c','c','c')
Future(a)(t1)

```

WEAK UNTIL 

a has to hold at least until b holds, if b never holds, then a must remain true forever 

a W b ≡ (a U b) ∨ G a 

```{r}
Weak_Until = function(exp1,exp2)
{
  f = function(t)
  {
    return(disjunction(Until(exp1,exp2),Global(exp1))(t))
  }
  return(f)
}

### TEST 

t = list('a','a','a','a')
Weak_Until(a,b)(t)

t1 = list('a','b','c')
Weak_Until(a,b)(t)
```

RELEASE 

a R b : b has to be true until and including the point where a becomes true, if a never becomes true, b must remain true forever 

b holds up to and including when a holds

a R b ≡ ¬(¬a U ¬b)

```{r} 
Release = function(exp1,exp2)
{
  f = function(t)
  {
    return(negation(Until(negation(exp1),negation(exp2)))(t))
  }
  return(f)
}

t = list('b','b','b','ab','c')
Release(a,b)(t)

t1 = list('b','b','b','b','b')
Release(a,b)(t1) #if a never becomes from, b remains true forever 
```

MIGHTY RELEASE 

b holds up to and including when a holds, and a must hold at some point in the future

a M b ≡ (a R b) ∧ F a

```{r}
Mighty_Release = function(exp1,exp2)
{
  f = function(t)
  {
    return(conjunction(Release(exp1,exp2),Future(exp1))(t))
  }
  return(f)
}

###

t = list('a','a','a','ab','c','c')
Mighty_Release(b,a)(t)

t1 = list('b','b','c','c')
Mighty_Release(b,a)(t1) # False beccause b must occur!
```


####

calvin's code: 

```{r}

calvin.implication = function(e1,e2)
{
  f = function(t)
  {
    if(e1(t))
    {
      return(e2(t))
    }
    return(TRUE)
  }
  return(f)
}

###

#test 

neXt(calvin.implication(b,a),3)(t)

```


```{r}
calvin.global = function(e)
{
  f = function(t)
    {
    len = length(t)
    if(len == 1)
    {
      return(e(1))
    }
    return(e(t) && calvin.global(e)(t[2:len]))
    }
  return(f)
}


```

```{r}
calvin.future = function(e)
{
 f = function(t)
 {
   len = length(t)
   if (len ==1)
   {
     return(e(t))
   }
   return(e(t) || calvin.futre(e)(t[2:len]))
 }
}


```

```{r}
calvin.release = function(e1,e2)
{
  f = function(t)
  {
    len = length(t)
    if (e1(t) && e2(t))
    {
      return(TRUE)
    }
    if(len > 1)
    {
      return(e2(t) && calvin.release(e1,e2)(t[2:len]))
    }
    return(FALSE)
  }
  return(f)
}

calvin.release(Xa,b)(t)

```


```{r}
calvin.mightyrelease = function(e1,e2)
{
  f = function(t)
  {
    len = lengh(t)
    if (e1(t) && e(t))
    {
      return(TRUE)
    }
    if(len > 1)
    {
      return(e2(t) && calvin.mightyrelease(e1,e2)(t[2:len]))
    }
    return(FALSE)
  }
  return(f)
}
```


weak until 
```{r}
calvin.until <-function(e1,e2)
{
  f <- function(t)
  {
    len = length(t)
    if (e2(t)){
      return(TRUE)
    } else if(e1(t) && len > 1){
      return(f(t[2:len]))
    } else {
      return(e1(t))
    }
  }
  return(f)
}

calvin.until(a,b)(t)

```


